---
title: "Connect RStudio to Python"
author: "Adrian Rus"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here are the steps to connect RStudio to Python:

1. Install R and RStudio: Make sure you have both R and RStudio installed on your computer. You can download and install them from their official websites.

2. Install Python: Ensure you have Python installed on your system. You can download Python from the official Python website or use a distribution like Anaconda, which includes many scientific libraries.

3. Install Reticulate Package: Open RStudio and create a new R script or R Markdown document. In the R script, install the "reticulate" package if you haven't already. You can do this with the following command:

```{r}
install.packages("reticulate")
```

4. Load the Reticulate Package: Load the "reticulate" package by using the library 

```{r}
library(reticulate)

```

5. Test Python Integration: To test if Python is integrated correctly, you can run a simple Python command from your R script:

```{r}
py_run_string("print('Hello from Python!')")

```

6. Running Python Code: You can now use Python code in your RStudio environment. Simply use the py_run_string or py_run_file functions to execute Python code.

For example:

```{r}
result <- py_run_string("2 + 2")
print(result)

```

################################################################################# 

